\emph{On Logics Extended with Embedding-Closed Quantifiers}

### 2020-11-08 paper.tex
Generalize the stabilization lemma to interpretations

\begin{lemma}\label{stabil}
Let $\tau$ be a finite relational vocabulary,
$\mathcal{Q}$ a finite set of embedding-closed quantifiers of finite width,
and $\varphi \in \mathcal{L}_{\infty\omega}^{\omega}(\mathcal{Q})[\tau]$ a sentence.
If $\mathcal{K}$ is a set of quasi-homogeneous $\tau$-structures, then there is
a structure $\mathfrak{A} \in \mathcal{K}$ that stabilizes $\varphi$ in $\mathcal{K}$.
\end{lemma}
\begin{proof}
Assume to the contrary that there is no such structure.
Then there is a function $F : \mathcal{K}\rightarrow\mathcal{K}$ such that
$\mathfrak{A} \leq F(\mathfrak{A})$ and
$\mathfrak{A} \vDash\varphi \nLeftrightarrow F(\mathfrak{A}) \vDash \varphi$ for
all $\mathfrak{A} \in \mathcal{K}$.
Now let $\mathfrak{A}_0 \in \mathcal{K}$ and define
$\mathfrak{A}_{k+1} = F(\mathfrak{A}_k)$.
Then $(\mathfrak{A}_i)_{i<\omega}$ is a chain of quasi-homogeneous structures in
which $\varphi$ does not stabilize which contradicts Theorem \ref{finite}.
\end{proof}

>>>>

\begin{lemma}\label{stabil}
Let $\tau$ and $\sigma$ be finite relational vocabularies and
$(\Psi, (\psi_R)_{R \in \sigma})$ an 
$\mathcal{L}_{\infty \omega}(\mathcal{Q}_{\emb})$-interpretation of $\sigma$ in
$\tau$.
Suppose $\mathcal{Q}$ is a finite set of embedding-closed quantifiers of finite width
and $\varphi \in \mathcal{L}_{\infty\omega}^{\omega}(\mathcal{Q})[\sigma]$ a sentence.
Let $\mathcal{K}$ be a set of quasi-homogeneous $\tau$-structures and write
\[
	\Psi(\mathcal{K}) = \{\Psi(\mathfrak{A}) \colon \mathfrak{A} \in \mathcal{K}\}.
\]
There is a structure $\mathfrak{A} \in \mathcal{K}$ such that $\Psi(\mathfrak{A})$
stabilizes $\varphi$ in $\Psi(\mathcal{K})$.
\end{lemma}
\begin{proof}
Assume to the contrary that there is no such structure.
Then there is a function $F : \mathcal{K} \rightarrow \mathcal{K}$ such that
$\Psi(\mathfrak{A}) \leq \Psi(F(\mathfrak{A}))$ and
$\Psi(\mathfrak{A}) \vDash\varphi \nLeftrightarrow \Psi(F(\mathfrak{A})) \vDash \varphi$ 
for all $\mathfrak{A} \in \mathcal{K}$.
Now let $\mathfrak{A}_0 \in \mathcal{K}$ and define
$\mathfrak{A}_{k+1} = F(\mathfrak{A}_k)$.
Then $(\Psi(\mathfrak{A}_i))_{i<\omega}$ is a chain, with all $\mathfrak{A}_i$
being quasi-homogeneous, that does not stabilize $\varphi$ which contradicts 
Theorem \ref{finite}.
\end{proof}
